### 2014-10-29 MS_revised.tex
table 2

\texttt{Table 2.} Differences in rates estimated by MEDUSA on the MCC
tree from Wahlberg and the MultiMEDUSA approach on 1000 random trees
from the posterior distribution.

@@

\section*{Tables}
% 
% See introductory notes if you wish to include sideways tables.
%
% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements. Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
%
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

\begin{table}[!h]
\caption{\bf{Significant net diversification rate shifts found in the MEDUSA analysis of the Nymphalid maximum clade credibility tree.}}
\begin{tabular}{lllllll}
Shift N$^\circ$ & Split.Node & Model & r          & LnLik.part & AICc     & Taxa                                                       \\
1               & 399        & yule  & 0.092459   & -1055.957  &          & Nymphalidae (root)                                         \\
2               & 691        & bd    & 0.054129   & -406.3703  &          & Limenitidinae + Heliconiinae                               \\
3               & 299        & yule  & 0.311199   & -6.3058    &          & \emph{Ypthima}                                             \\
4               & 224        & yule  & 0.290989   & -6.2601    &          & \emph{Charaxes}                                            \\
5               & 750        & yule  & 0.186913   & -147.4146  &          & Oleriina + Ithomiina + Napeogenina + Dircennina + Godyrina \\
6               & 405        & yule  & 0.116252   & -555.0276  &          & Satyrini                                                   \\
7               & 495        & yule  & 0.064656   & -124.9143  &          & Coenonymphina                                              \\
8               & 609        & yule  & 0.240562   & -35.0908   &          & Phyciodina in part                                         \\
9               & 787        & bd    & 0.042332   & -43.7819   &          & Danaini in part                                            \\
10              & 231        & yule  & 0.209416   & -4.7955    &          & \emph{Coenonympha}                                         \\
11              & 478        & yule  & 0.311684   & -9.2218    &          & \emph{Caeruleuptychia} + \emph{Magneuptychia}              \\
12              & 659        & yule  & 0.219253   & -11.2686   &          & \emph{Callicore} + \emph{Diaethria}                        \\
13              & 444        & yule  & 0.220615   & -43.7812   &          & Satyrina                                                   \\
14              & 524        & yule  & 0.190754   & -26.0651   &          & Mycalesina                                                 \\
15              & 355        & yule  & 0.234041   & -6.2013    &          & \emph{Pedaliodes}                                          \\
16              & 714        & yule  & 0          & 0          &          & \emph{Dryas} + \emph{Dryadula}                             \\
17              & 377        & yule  & 0.311671   & -4.1986    &          & \emph{Taenaris}                                            \\
18              & 688        & yule  & 0.024724   & -17.5256   &          & Pseudergolinae                                             \\
19              & 583        & yule  & 0          & 0          & 5090.492 & \emph{Anaeomorpha} + \emph{Hypna}                                       
\end{tabular}
\begin{flushleft}Split.Node=node number, Model=preferred diversification model by MEDUSA, r=net diversification rate, LnLik.part=log likelihood value.
\end{flushleft}
\end{table}

>>>>

@@

\section*{Tables}
\begin{table}[!h]
\caption{\bf{Significant net diversification rate shifts found in the MEDUSA analysis of the Nymphalid maximum clade credibility tree.}}
\begin{tabular}{lccrrcl}
Shift N$^\circ$ & Split.Node & Model & r          & LnLik.part & AICc     & Taxa                                                       \\
1               & 399        & yule  & 0.092459   & -1055.957  &          & Nymphalidae (root)                                         \\
2               & 691        & bd    & 0.054129   & -406.3703  &          & Limenitidinae + Heliconiinae                               \\
3               & 299        & yule  & 0.311199   & -6.3058    &          & \emph{Ypthima}                                             \\
4               & 224        & yule  & 0.290989   & -6.2601    &          & \emph{Charaxes}                                            \\
5               & 750        & yule  & 0.186913   & -147.4146  &          & Oleriina + Ithomiina + Napeogenina + Dircennina + Godyrina \\
6               & 405        & yule  & 0.116252   & -555.0276  &          & Satyrini                                                   \\
7               & 495        & yule  & 0.064656   & -124.9143  &          & Coenonymphina                                              \\
8               & 609        & yule  & 0.240562   & -35.0908   &          & Phyciodina in part                                         \\
9               & 787        & bd    & 0.042332   & -43.7819   &          & Danaini in part                                            \\
10              & 231        & yule  & 0.209416   & -4.7955    &          & \emph{Coenonympha}                                         \\
11              & 478        & yule  & 0.311684   & -9.2218    &          & \emph{Caeruleuptychia} + \emph{Magneuptychia}              \\
12              & 659        & yule  & 0.219253   & -11.2686   &          & \emph{Callicore} + \emph{Diaethria}                        \\
13              & 444        & yule  & 0.220615   & -43.7812   &          & Satyrina                                                   \\
14              & 524        & yule  & 0.190754   & -26.0651   &          & Mycalesina                                                 \\
15              & 355        & yule  & 0.234041   & -6.2013    &          & \emph{Pedaliodes}                                          \\
16              & 714        & yule  & 0          & 0          &          & \emph{Dryas} + \emph{Dryadula}                             \\
17              & 377        & yule  & 0.311671   & -4.1986    &          & \emph{Taenaris}                                            \\
18              & 688        & yule  & 0.024724   & -17.5256   &          & Pseudergolinae                                             \\
19              & 583        & yule  & 0          & 0          & 5090.492 & \emph{Anaeomorpha} + \emph{Hypna}                                       
\end{tabular}
\begin{flushleft}Split.Node=node number, Model=preferred diversification model by MEDUSA, r=net diversification rate, LnLik.part=log likelihood value.
\end{flushleft}
\end{table}

\begin{table}[!h]
    \caption{\bf{Differences in rates estimated by MEDUSA on the MCC
tree from Wahlberg and the MultiMEDUSA approach on 1000 random trees
from the posterior distribution.}}
\begin{tabular}{lcrr}
Split.Node & rate by MEDUSA & Median rate by MultiMEDUSA & probability of being recovered \\
1          & 0.090          & not found                  & 0.000                          \\
2          & 0.054          & -0.030                     & 0.864                          \\
3          & 0.311          & 0.219                      & 0.961                          \\
4          & 0.290          & 0.212                      & 0.996                          \\
5          & 0.187          & 0.101                      & 0.927                          \\
6          & 0.116          & 0.039                      & 0.131                          \\
7          & 0.064          & -0.052                     & 0.195                          \\
8          & 0.240          & 0.166                      & 0.319                          \\
9          & 0.042          & -0.049                     & 0.897                          \\
10         & 0.209          & 0.149                      & 0.619                          \\
11         & 0.311          & 0.208                      & 0.831                          \\
12         & 0.219          & 0.135                      & 0.911                          \\
13         & 0.220          & 0.117                      & 0.276                          \\
14         & 0.190          & 0.115                      & 0.379                          \\
15         & 0.234          & 0.127                      & 0.825                          \\
16         & 0.000          & -0.005                     & 0.659                          \\
17         & 0.311          & 0.248                      & 0.785                          \\
18         & 0.024          & -0.064                     & 0.024                          \\
19         & 0.000          & -0.087                     & 0.381                         
\end{tabular}
\end{table}
% 
% See introductory notes if you wish to include sideways tables.
%
% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements. Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
%
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}
